\texttt{ggmatplot}: An R package for data visualization on wide-format data

### 2022-05-07 Paper/paper.Rmd
add comments in the draft

@@

```{r tab3, echo = FALSE}
head(SnowGR[, 1:11]) %>% 
  mutate(Jan = as.character(Jan)) %>% 
  replace_na(list(Jan = ".")) %>% 
  table_styling(caption = 'The first 6 rows and 11 columns of the snowfall data for Grand Rapids, Michigan in the `mosaicData` R pacakge (Prium, Kaplan \\& Horton, 2021).',
                align = "r")
```

@@

@@

@@

>>>>

*Regarding the question from Francis, I don't know if long format or wide format data is well defined in the literature. If it is, we definitely can mention it. If not, do we need to define it? --commented by XL*

@@

```{r tab3, echo = FALSE}
head(SnowGR[, 1:11]) %>% 
  mutate(Jan = as.character(Jan)) %>% 
  replace_na(list(Jan = ".")) %>% 
  table_styling(caption = 'The first 6 rows and 11 columns of the snowfall data for Grand Rapids, Michigan in the R pacakge  \texttt{mosaicData} (Prium, Kaplan \\& Horton, 2021).',
                align = "r")
```

@@

*In example 1, should X lab be restaurant or one type rating? The one made by ggmatplot is different from the one made by ggplot. Currently, the plot does not show a clear relationship between various types and the overall rating. Is it better to compare the ratings among restaurants?  -- commented by XL*

@@

*Now the color and fill has been removed by default for boxplot by default, there is no legend. We may need to change the demonstration of Example 2. -- commented by XL*
*Another question is that only the github version has such setting. Do I need to submit the new version to CRAN? -- commented by XL*

@@

*The other option is the density plot which can not be done by matplot--commented by XL. But since there are too many months, it might not be a good idea. -- commented by XL*

### 2022-05-07 Paper/paper.tex
add comments in the draft

% --- Header / Footer ---------------------------------------------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
%\renewcommand{\headrulewidth}{0.50pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{\hspace{-0.75cm}\includegraphics[width=5.5cm]{/home/fkch/R/x86_64-pc-linux-gnu-library/3.6/rticles/rmarkdown/templates/joss/resources/JOSS-logo.png}}
\fancyhead[C]{}
\fancyhead[R]{}
\renewcommand{\footrulewidth}{0.25pt}

@@

@@

\caption{\label{tab:tab3}The first 6 rows and 11 columns of the snowfall data for Grand Rapids, Michigan in the `mosaicData` R pacakge (Prium, Kaplan \& Horton, 2021).}
\centering
\begin{tabular}[t]{rrrrrrrrrrr}
\toprule
SeasonStart & SeasonEnd & Jul & Aug & Sep & Oct & Nov & Dec & Jan & Feb & Mar\\
\midrule
1893 & 1894 & 0 & 0 & 0 & 0.0 & 8.0 & 24.9 & 12.5 & 6.8 & 4.8\\
1894 & 1895 & 0 & 0 & 0 & 0.0 & 7.5 & 5.3 & 21.5 & 8.0 & 22.5\\
1895 & 1896 & 0 & 0 & 0 & 0.4 & 23.2 & 15.0 & . & 8.5 & 2.0\\
1896 & 1897 & 0 & 0 & 0 & 0.2 & 8.0 & 8.0 & 4.9 & 11.2 & 12.0\\
1897 & 1898 & 0 & 0 & 0 & 0.0 & 1.4 & 8.0 & 15.5 & 29.5 & 0.0\\
1898 & 1899 & 0 & 0 & 0 & 0.0 & 18.5 & 18.0 & 20 & 3.4 & 16.0\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-mosaicData}{}}%
Pruim, R., Kaplan, D., \& Horton, N. (2021). \emph{mosaicData: Project
MOSAIC data sets}. Retrieved from
\url{https://CRAN.R-project.org/package=mosaicData}

\leavevmode\vadjust pre{\hypertarget{ref-rstats}{}}%
R Core Team. (2021). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}

\leavevmode\vadjust pre{\hypertarget{ref-Wickham2010-kt}{}}%
Wickham, H. (2010). A layered grammar of graphics. \emph{Journal of
computational and graphical statistics: a joint publication of American
Statistical Association, Institute of Mathematical Statistics, Interface
Foundation of North America}.

\leavevmode\vadjust pre{\hypertarget{ref-Wickham2014-gy}{}}%
Wickham, H. (2014). Tidy data. \emph{Journal of Statistical Software},
\emph{59}(10), 1--23.
doi:\href{https://doi.org/10.18637/jss.v059.i10}{10.18637/jss.v059.i10}

\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}.
Springer-Verlag New York. Retrieved from
\url{https://ggplot2.tidyverse.org}

\leavevmode\vadjust pre{\hypertarget{ref-Wickham2019}{}}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D.,
François, R., Grolemund, G., et al. (2019). Welcome to the {tidyverse}.
\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
doi:\href{https://doi.org/10.21105/joss.01686}{10.21105/joss.01686}

\leavevmode\vadjust pre{\hypertarget{ref-Wilkinson2005-oz}{}}%
Wilkinson, L. (2005). \emph{The grammar of graphics}. Springer.

>>>>

% --- Header / Footer ---------------------------------------------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
%\renewcommand{\headrulewidth}{0.50pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{\hspace{-0.75cm}\includegraphics[width=5.5cm]{/Library/Frameworks/R.framework/Versions/4.1/Resources/library/rticles/rmarkdown/templates/joss/resources/JOSS-logo.png}}
\fancyhead[C]{}
\fancyhead[R]{}
\renewcommand{\footrulewidth}{0.25pt}

@@

\emph{Regarding the question from Francis, I don't know if long format
or wide format data is well defined in the literature. If it is, we
definitely can mention it. If not, do we need to define it? --commented
by XL}

@@

\caption{\label{tab:tab3}The first 6 rows and 11 columns of the snowfall data for Grand Rapids, Michigan in the R pacakge   exttt{mosaicData} (Prium, Kaplan \& Horton, 2021).}
\centering
\begin{tabular}[t]{rrrrrrrrrrr}
\toprule
SeasonStart & SeasonEnd & Jul & Aug & Sep & Oct & Nov & Dec & Jan & Feb & Mar\\
\midrule
1893 & 1894 & 0 & 0 & 0 & 0.0 & 8.0 & 24.9 & 12.5 & 6.8 & 4.8\\
1894 & 1895 & 0 & 0 & 0 & 0.0 & 7.5 & 5.3 & 21.5 & 8.0 & 22.5\\
1895 & 1896 & 0 & 0 & 0 & 0.4 & 23.2 & 15.0 & . & 8.5 & 2.0\\
1896 & 1897 & 0 & 0 & 0 & 0.2 & 8.0 & 8.0 & 4.9 & 11.2 & 12.0\\
1897 & 1898 & 0 & 0 & 0 & 0.0 & 1.4 & 8.0 & 15.5 & 29.5 & 0.0\\
1898 & 1899 & 0 & 0 & 0 & 0.0 & 18.5 & 18.0 & 20 & 3.4 & 16.0\\
\bottomrule
\end{tabular}
\end{table}

@@

\emph{In example 1, should X lab be restaurant or one type rating? The
one made by ggmatplot is different from the one made by ggplot.
Currently, the plot does not show a clear relationship between various
types and the overall rating. Is it better to compare the ratings among
restaurants? -- commented by XL}

@@

\emph{Now the color and fill has been removed by default for boxplot by
default, there is no legend. We may need to change the demonstration of
Example 2. -- commented by XL} \emph{Another question is that only the
github version has such setting. Do I need to submit the new version to
CRAN? -- commented by XL}

@@

\emph{The other option is the density plot which can not be done by
matplot--commented by XL. But since there are too many months, it might
not be a good idea. -- commented by XL}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-mosaicData}{}%
Pruim, R., Kaplan, D., \& Horton, N. (2021). \emph{mosaicData: Project
MOSAIC data sets}. Retrieved from
\url{https://CRAN.R-project.org/package=mosaicData}

\leavevmode\hypertarget{ref-rstats}{}%
R Core Team. (2021). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-Wickham2010-kt}{}%
Wickham, H. (2010). A layered grammar of graphics. \emph{Journal of
computational and graphical statistics: a joint publication of American
Statistical Association, Institute of Mathematical Statistics, Interface
Foundation of North America}.

\leavevmode\hypertarget{ref-Wickham2014-gy}{}%
Wickham, H. (2014). Tidy data. \emph{Journal of Statistical Software},
\emph{59}(10), 1--23.
doi:\href{https://doi.org/10.18637/jss.v059.i10}{10.18637/jss.v059.i10}

\leavevmode\hypertarget{ref-Wickham2016}{}%
Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}.
Springer-Verlag New York. Retrieved from
\url{https://ggplot2.tidyverse.org}

\leavevmode\hypertarget{ref-Wickham2019}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D.,
François, R., Grolemund, G., et al. (2019). Welcome to the {tidyverse}.
\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
doi:\href{https://doi.org/10.21105/joss.01686}{10.21105/joss.01686}

\leavevmode\hypertarget{ref-Wilkinson2005-oz}{}%
Wilkinson, L. (2005). \emph{The grammar of graphics}. Springer.
